---
title: "Introduction to Rd2md"
author: "J. Busch"
date: "`r Sys.Date()`"
output: 
  rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Introduction Rd2md}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Reference Manual To PDF

The Reference Manual of a package exported as PDF is a terminal command shipped
with R.

```
R CMD Rd2pdf
```

However, pdf versions are quite static and nothing can really be done with it. 

The single .Rd files are well structured and can easily parsed to .md files. Thanks to [jbryer](https://github.com/jbryer/Rd2markdown) to publish the relevant code.

These base functionalities were used (and changed/extended) to replicate a
Reference Manual in markdown format.

# Reference Manual To Markdown

The main functionality of this package is to create the reference manual in
markdown format. 

However, packages can be available in either source format (from development)
or as binary packages (from libraries). This package shall extract from both
possible sources the documentation files and create the reference manual.

The output file will have the name following the naming convention:
`"Reference_manual_" + PACKAGE_NAME + ".md"`

## From Source

The prerequisites are:

* Path to package source is known (root) and readable
* `man` directory with `.Rd` files is available
* Output directory is writeable

To create the reference manual from the package source, use the `type="src"`
parameter:

```{r, eval=FALSE}
ReferenceManual(pkg, outdir, type="src")
```

For the `pkg` variable, provide the **path** of the source code of the
package and the `outdir` can be any available directory path.

## From Binary

The prerequisites are:

* Path to package binaries (most likely library path) is known and readable
* `help` directory with `.rdb` file is available
* Output directory is writeable


To create the reference manual from the package binaries, use the `type="bin"`
parameter:

```{r, eval=FALSE}
ReferenceManual(pkg, outdir, type="bin")
```

E .g. a possible library path would
be `/usr/local/lib/R/site-library/Rd2md`.

