---
title: "Introduction to Rd2md"
author: "J. Busch"
date: "`r Sys.Date()`"
output: 
  rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Introduction Rd2md}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# PDF Reference Manual

The Reference Manual of a package exported as PDF is a terminal command shipped
with R. Given you are in the root of your package, the following will create
the PDF manual:

```
R CMD Rd2pdf -o ReferenceManual.pdf .
```

However, other formats are only possible converting a single Rd file to
html, LaTeX or text and there is no option to create a reference manual in
those formats.

This is where markdown comes in handy, as it can be further processed
easily into a wide variety of formats and is also a go-to format for static
website genererators.

# Markdown Reference Manual

The main functionality of this package is to create the reference manual in
markdown format. 

However, packages can be available in either source format (from development)
or as binary packages (from libraries). This package can extract the
documentation files from both and create the reference manual.

## From Package Source

The prerequisites are:

* Path to package source readable
* `man` directory with `.Rd` files is available
* `DESCRIPTION` file is available in package root
* Output directory is writeable

To create the reference manual from the package source, use:

```{r, eval=FALSE}
render_refman()
```

This will default to the current working directory being the package root and
the output file name to be `<pkg-name>.md`.

You can also specify the `pkg` variable and provide the **path** of the source
code of the package and the `output_file` can be any file path, including
file extension:

```{r, eval=FALSE}
render_refman(
  pkg = "path/to/package_root",
  output_file = "path/to/output/reference_manual.md"
)
```

## From Package Binary

The prerequisites are:

* Path to package binaries (most likely library path) is readable
* `help` directory with `.rdb` file is available
* `DESCRIPTION` file is available in package root
* Output directory is writeable

**Remark**: Package name must not be a directory in the current working
directory, otherwise the function will try to read the source from that
directory instead of searching the package in the R libraries.

To create the reference manual from the package binaries, use:

```{r, eval=FALSE}
render_refman(pkg = "<pkg-name>")
```

In this situation, the `pkg` variable should be given as the package name only,
without any path.
